Set-up
========================================================
Setup the bioconductor packages.
```{r}
source("http://bioconductor.org/biocLite.R")
# Install all core packages and update all installed packages
biocLite()

biocLite(c("GEOmetadb", "GEOquery"))

library("RSQLite")
```
Establish connection to the db:

```{r}
geo_con <- dbConnect(SQLite(),'GEOmetadb.sqlite')
```

```{r}
library(data.table)
```

```{r}
gse_table = data.table(dbReadTable(geo_con, 'gse'))
gpl_table = data.table(dbReadTable(geo_con, 'gpl'))
gse_gpl_table = data.table(dbReadTable(geo_con, 'gse_gpl'))
```
1)
=====================
"Use the GEOmetabd package to find all HCV gene expression data using the Illumina platform submitted by an investigator at Yale. This should be done with a single query, showing the title, the GSE accession number, the GPL accession number and the manufacturer and the description of the platform used."

Comment from Jun H: This looks good! The only suggestion I have would be to search for "Hepatitis C" in addition to "HCV" under the gse.title field.

```{r }
dbGetQuery(geo_con, "SELECT gse.title, gse.gse, gpl.gpl, gpl.manufacturer, gpl.description FROM (gse JOIN gse_gpl ON gse.gse=gse_gpl.gse) j JOIN gpl ON j.gpl=gpl.gpl WHERE gpl.Title LIKE '%Illumina%' AND gse.contact LIKE '%Institute: Yale %'  AND gse.Title LIKE '%HCV%' LIMIT 5;")
```

2)
=========================
"Reproduce your above query using the data.table package. Again, try to use a single line of code. [Hint: You first need to convert all db tables to data.table tables]."

Comment from Jun H: Again, this looks good; the results are the same as from your previous query. 
```{r}
merge( merge( (gse_table[like(contact,"Institute: Yale")][like(title, "HCV")]), gse_gpl_table, by = "gse",  suffixes = c(".gse_inner",".gse_gpl") ), gpl_table[like(title, "Illumina")], by = "gpl", suffixes = c(".gse", ".gpl") )[,list(title.gse, gse, gpl, manufacturer, description)]
```

