BIOSTAT-578 HW2 YUCHI CHANG
========================================================
Background reading:

Reading NCBI's GEO microarray file
http://www2.warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/

Setup the bioconductor packages.
```{r}
source("http://bioconductor.org/biocLite.R")
# Install all core packages and update all installed packages
biocLite()

biocLite(c("GEOmetadb", "GEOquery", "lumi", "limma"))



library("RSQLite")
library(GEOmetadb)
library(lumi)
library(limma)
library(data.table)
library(pheatmap)
```
Establish connection to the db:

```{r}
geo_con <- dbConnect(SQLite(),'GEOmetadb.sqlite')
```
=======================================
1. Get data for :
Qian, F., Bolen, C. R., Jing, C., Wang, X., Zheng, W., Zhao, H., et al. (2013). Impaired toll-like receptor 3-mediated immune responses from macrophages of patients chronically infected with hepatitis C virus. Clinical and Vaccine Immunology : CVI, 20(2), 146–155. doi:10.1128/CVI.00530-12


```{r}

dbGetQuery(geo_con, "SELECT gse.gse, gse.pubmed_id, gse.contributor FROM gse WHERE gse.title LIKE '%Impaired TLR3-mediated immune responses from macrophages of patients chronically infected with Hepatitis C virus%';")
library(GEOquery)

gse <- getGEO("GSE40812", destdir = "E:\\Users\\Chipooh\\Documents\\GitHub\\RachelYuChiChang")[[1]]
#gse <- getGEO("GSE40812", destdir = "E:\\Users\\Chipooh\\Documents\\GitHub\\RachelYuChiChang", GSEMatrix=FALSE)[[1]]

```

Select only macrophage elements. Add HCV and treatment columns.

```{r}
pd <- pData(gse)
mmpd <- pd[pd$source_name_ch1=="Monocyte-derived Macrophage",]
mmeset<-gse[,rownames(mmpd)]
#characteristic_ch1 indicates VL++ or VL--
#characteristic_ch1.2 indicates Mock or Poly IC
mmpd$HCV <- gsub(".*: ", "", mmpd$characteristics_ch1)
#mmpd$HCV <- ifelse(mmpd$HCV=="Neg", "-", "+")
mmpd$treatment <- tolower(gsub(".*: ", "", mmpd$characteristics_ch1.2))

```

Normalize data

```{r, cache=TRUE}

mmMatrix<-model.matrix(~0+HCV, mmpd)
mmfit<-lmFit(mmeset, mmMatrix)
mmebfit<-eBayes(mmfit)



```

```{r}
cont_matrix <- makeContrasts(HCVPos-HCVNeg, levels=mmMatrix)
fit2 <- contrasts.fit(mmfit, cont_matrix)
fit2 <- eBayes(fit2)
tt <- topTable(fit2, adjust = "fdr")

pheatmap(exprs(mmeset), kmeans_k = 43)
```